The SMT Competition 2015--2018

### 2019-04-15 2018/report/SMT-COMP.tex
Report: More outlook

\begin{itemize}
	\item the inclusion of {\tt check-sat} commands with unknown status in
  the \apptrack, 
  	\item the removal of non-competitive divisions and the filtering of benchmarks to exclude those seen as \emph{trivial} (taken as those solved by all competitors in the previous competition in less than 1 second)  
  	\item the introduction of a new experimental \emph{model validation track} with a single QF\_BV division where the models produced by solvers are checked,
	\item the introduction of a new \emph{industrial challenge track} consisting of unsolved benchmarks submitted specifically for the track, and
	\item the removal of the notion of competition-wide scoring.
\end{itemize}

>>>>

\begin{itemize}
  \item the introduction of new \emph{additional scores} for
    satisfiable/unsatisfiable benchmarks and benchmarks solved within 24
    seconds in the \maintrack,
	\item the inclusion of {\tt check-sat} commands with unknown status in
  the \apptrack,
  \item the removal of \emph{non-competitive divisions} and the filtering of
    benchmarks to exclude those seen as \emph{trivial} (taken as those solved
    by all competitors in the previous competition in less than 1 second),
  \item the introduction of a new experimental \emph{model validation track}
    with a single QF\_BV division where the models produced by solvers are
    checked,
  \item the introduction of a new \emph{industrial challenge track} consisting
    of unsolved benchmarks submitted specifically for the track,
  \item the replacement of the notion of \emph{competition-wide scoring} with
    awards that do not attempt to compare divisions.
\end{itemize}
